### 2015-05-29 Irregulares/AA-2015-26273/Irregulares.tex
...

%% LyX 2.0.0 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,traditabstract]{aa}
\usepackage[varg]{txfonts}
%\usepackage[english,brazilian]{babel}
\usepackage[T1]{fontenc}
\setcounter{tocdepth}{3}
\usepackage{prettyref}
\usepackage{array}
\usepackage{rotating}
\usepackage{float}
\usepackage{multirow}
\usepackage{amstext}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{subfigure}
\usepackage{gensymb}
\usepackage{longtable}
%\usepackage{setspace}
%
%\usepackage{etoolbox}
%\AtBeginEnvironment{longtable}{\singlespacing}
%\setlength{\LTcapwidth}{\linewidth}

@@

\date{Received ; accepted }

@@

\begin{table*}
\caption{\label{Tab: sample-cds} CDS data table sample for Himalia.}
\begin{centering}
\begin{tabular}{ccccccccc}
\hline 
%\multicolumn{9}{c}{Himalia} \tabularnewline
\hline
% & \multicolumn{2}{c}{Mean errors} & Nr & Nr &  UCAC4       \tabularnewline
\multicolumn{2}{c}{RA  (ICRS)  Dec} & RA error & Dec error & Epoch & Mag & Filter & Telescope & \textbf{IAU code} \tabularnewline
\multicolumn{1}{l}{\ h \ m \ \ \ s} & \multicolumn{1}{l}{\ \ \ $\degree$ \ \ \ $\arcmin$ \ \ \ $\arcsec$} &   (mas)   &   (mas)  & (jd) & & & & \tabularnewline
\hline
 16 59 11.6508 & -22 00 44.855 &  17 &  12 & 2454147.78241319 &   16.0 &    C &      BC & \textbf{874} \tabularnewline
 16 59 11.6845 & -22 00 44.932 &  17 &  12 & 2454147.78332384 &   15.8 &    C &      BC & \textbf{874} \tabularnewline
 16 59 11.7181 & -22 00 44.978 &  17 &  12 & 2454147.78422477 &   16.0 &    C &      BC & \textbf{874} \tabularnewline
 16 59 11.7818 & -22 00 45.143 &  17 &  12 & 2454147.78602662 &   15.9 &    C &      BC & \textbf{874} \tabularnewline
 16 59 11.8188 & -22 00 45.232 &  17 &  12 & 2454147.78693750 &   16.0 &    C &      BC & \textbf{874} \tabularnewline
 17 17 11.0344 & -22 47 19.415 &  30 &  24 & 2454205.63885463 &   16.1 &        U &      BC & \textbf{874} \tabularnewline
 17 17 11.0270 & -22 47 19.381 &  30 &  24 & 2454205.63959167 &   16.1 &        U &      BC & \textbf{874} \tabularnewline
 17 17 11.0258 & -22 47 19.366 &  30 &  24 & 2454205.64031875 &   16.1 &        U &      BC & \textbf{874} \tabularnewline
 17 17 11.0192 & -22 47 19.417 &  30 &  24 & 2454205.64104583 &   16.1 &        U &      BC & \textbf{874} \tabularnewline
\hline
\end{tabular}
\par\end{centering}
This sample corresponds to 9 observations of Himalia from February 16, 2007 and April 15, 2007. Tables contain the topocentric ICRS coordinates of the irregular satellites, the position error estimated from the dispersion of the ephemeris offsets of the night of observation, the UTC time of the frame's mid-exposure in Julian date, the estimated magnitude, the filter used, the telescope origin and correspondent IAU code. The filters may be U, B, V, R or I following the Johnson system; C stands for clear (no filter used), resulting in a broader R band magnitude, RE for the broad-band R filter ESO\#844 with $\lambda_{c} = 651.725$ nm and $\Delta\lambda = 162.184 $ nm (full width at half maximum) and "un" for unknown filter. E, OH, PE, BC and Z stand for the ESO, OHP, Perkin-Elmer, Bollen \& Chivens and Zeiss telescopes, respectively.
\end{table*}

>>>>

%% LyX 2.0.0 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,traditabstract]{aa}
\usepackage[varg]{txfonts}
%\usepackage[english,brazilian]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\setcounter{tocdepth}{3}
\usepackage{prettyref}
\usepackage{array}
\usepackage{rotating}
\usepackage{float}
\usepackage{multirow}
\usepackage{amstext}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{subfigure}
\usepackage{gensymb}
\usepackage{longtable}
%\usepackage{setspace}
%
%\usepackage{etoolbox}
%\AtBeginEnvironment{longtable}{\singlespacing}
%\setlength{\LTcapwidth}{\linewidth}

@@

\date{Received: Abr 08, 2015; accepted: May 06, 2015}

@@

\begin{table*}
\caption{\label{Tab: sample-cds} CDS data table sample for Himalia.}
\begin{centering}
\begin{tabular}{ccccccccc}
\hline 
%\multicolumn{9}{c}{Himalia} \tabularnewline
\hline
% & \multicolumn{2}{c}{Mean errors} & Nr & Nr &  UCAC4       \tabularnewline
\multicolumn{2}{c}{RA  (ICRS)  Dec} & RA error & Dec error & Epoch & Mag & Filter & Telescope & IAU code \tabularnewline
\multicolumn{1}{l}{\ h \ m \ \ \ s} & \multicolumn{1}{l}{\ \ \ $\degree$ \ \ \ $\arcmin$ \ \ \ $\arcsec$} &   (mas)   &   (mas)  & (jd) & & & & \tabularnewline
\hline
 16 59 11.6508 & -22 00 44.855 &  17 &  12 & 2454147.78241319 &   16.0 &    C &      BC & 874 \tabularnewline
 16 59 11.6845 & -22 00 44.932 &  17 &  12 & 2454147.78332384 &   15.8 &    C &      BC & 874 \tabularnewline
 16 59 11.7181 & -22 00 44.978 &  17 &  12 & 2454147.78422477 &   16.0 &    C &      BC & 874 \tabularnewline
 16 59 11.7818 & -22 00 45.143 &  17 &  12 & 2454147.78602662 &   15.9 &    C &      BC & 874 \tabularnewline
 16 59 11.8188 & -22 00 45.232 &  17 &  12 & 2454147.78693750 &   16.0 &    C &      BC & 874 \tabularnewline
 17 17 11.0344 & -22 47 19.415 &  30 &  24 & 2454205.63885463 &   16.1 &        U &      BC & 874 \tabularnewline
 17 17 11.0270 & -22 47 19.381 &  30 &  24 & 2454205.63959167 &   16.1 &        U &      BC & 874 \tabularnewline
 17 17 11.0258 & -22 47 19.366 &  30 &  24 & 2454205.64031875 &   16.1 &        U &      BC & 874 \tabularnewline
 17 17 11.0192 & -22 47 19.417 &  30 &  24 & 2454205.64104583 &   16.1 &        U &      BC & 874 \tabularnewline
\hline
\end{tabular}
\par\end{centering}
This sample corresponds to 9 observations of Himalia from February 16, 2007 and April 15, 2007. Tables contain the topocentric ICRS coordinates of the irregular satellites, the position error estimated from the dispersion of the ephemeris offsets of the night of observation, the UTC time of the frame's mid-exposure in Julian date, the estimated magnitude, the filter used, the telescope origin and correspondent IAU code. The filters may be U, B, V, R or I following the Johnson system; C stands for clear (no filter used), resulting in a broader R band magnitude, RE for the broad-band R filter ESO\#844 with $\lambda_{c} = 651.725$ nm and $\Delta\lambda = 162.184 $ nm (full width at half maximum) and "un" for unknown filter. E, OH, PE, BC and Z stand for the ESO, OHP, Perkin-Elmer, Bollen \& Chivens and Zeiss telescopes, respectively.
\end{table*}
